---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Yuriy Lisovets"
date: 'March, 17 2021 '
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(dplyr)
library(ggplot2)
data <- read.csv("Shine_app/Data/data.csv", stringsAsFactors = FALSE)
```


## Course Project

- This is the final presentation for the Course Project
- The course is focused on Developing Data Products
- The main objective of the project is to write a Shiny application

You may access my Shinyapp page at https://yuriy.shinyapps.io/Quadrant_sales_analysis/.

Source code for ui.R and server.R files are available on the GitHub https://github.com/YLisovets/DataProducts

## Application Overview

This app solves a real business problem - quickly identify the best performing categories/items in sales dataset using quadrant analysis.

A quadrant chart is nothing but a scatter plot that has four components. Each quadrant upholds data points that have similar characteristics.

Our objective is to evaluate the performance of various sub-categories based on sales and profit metrics.

For analysis we can choose shop (or all shops) and product category (or all categories), and also specify aggregate level.

Results table we can download as Excel file.

## Data Used

The real business data used for this application we load from csv - file. Our dataset have 20206 rows with 6 variables.


```{r, echo=TRUE}
head(data)
```

## Result Example
```{r, echo = FALSE}
data%>%
    filter(Category == 2, Shop == "Shop_2") %>% 
    group_by(Item) %>% 
    summarise(sale = sum(Sales),
               marg = sum(Gr_Margin)) %>%
    mutate(Quadrant = ifelse(marg >= mean(marg),
                             ifelse(sale >= mean(sale), "Star Performers", "Cash Machines"),
                                 ifelse(sale >= mean(sale), "Core Traffic", "Revision!"))) %>% 
    ggplot(aes(x = marg, y = sale, color = Quadrant)) +
            geom_point() +
            geom_hline(aes(yintercept = mean(sale))) +
            geom_vline(aes(xintercept = mean(marg))) +
            labs(x = 'Gross Margin', y = 'Sales', color = '') +
            theme_bw()
```

